Jeff A. Stuart, Pavan Balaji, and John D. Owens {\it Extending MPI to Accelerators}. Submitted to {\it PACT Workshop Series 2011: First Workshop on Architectural Support for Big Data (ASBD 2011)}.

Kshitij Gupta, Jeff A. Stuart, and John D. Owens {\it A Study of Persistent Threads Style GPU Programming for GPGPU Workloads}. Submitted to {\it PPoPP 2011}.

Jeff A. Stuart and John D. Owens. {\it Efficient Synchronization Primitives for GPUs}. Submitted to {\it ASPLOS 2012}.

Jeff A. Stuart and John D. Owens. {\it Multi-GPU MapReduce on GPU Clusters}. {\it International Parallel and Distributed Processing Symposium (IPDPS)}, May 2011.

Jeff A. Stuart, Michael Cox, and John D. Owens. {\it GPU-to-CPU Callbacks}. In {\it UnConventional High-Performance Computing 2010} as part of the {\it EuroPar 2010 Workshop Series}. September 2010.

Jeff A. Stuart, Cheng-Kai Chen, Kwan-Liu Ma, and John D. Owens. {\it Multi-GPU Volume Rendering using MapReduce}. In {\it MAPREDUCE '10, The First International Workshop on MapReduce and its Applications.} as part of the {\it High-Performance and Distributed Computing 2010 Workshop Series}. June 2010.

Jeff A. Stuart and John D. Owens. {\it Message Passing on Data-Parallel Architectures}. In {\it Proceedings of the 23rd IEEE International Parallel and Distributed Processing Symposium}, May 2009.

Brian Budge, Tony Bernardin, Jeff A. Stuart, Shubhabrata Sengupta, Kenneth I. Joy, and John D. Owens. {\it Out-of-core Data Management for Path Tracing on Hybrid Resources}. In {\it Computer Graphics Forum (Proceedings of Eurographics 2009)}, 28(2):385--396, April 2009.

Jeff A. Stuart, Joseph Jaquish, Scott Bassett, Frederick Harris, and William Sherman. {\it An Interactive Visualization Method for Integrating Digital Elevation Models and Geographic Information Systems Vector Layers}.  In {\it Proceedings of International Symposium of Visual Computing 2005},  December 5--7, 2005. Lake Tahoe, NV.

Jeff A. Stuart. {\it A Unified Approach for Cross-Platform Software Development}. Master’s Thesis, University of Nevada, Reno.

John D. Studebaker, Justin T. Gerthoffer, David D. Colborne, Jeff A.  Stuart, Frederick C. Harris, Jr. {\it Thraxion: Three-Dimensional Action Simulator}. In {\it Proceedings of the 2005 International Conference on Software Engineering Research and Practice (SERP ‘05)}, June 27--30, 2005, Las  Vegas, NV.

Jeff A. Stuart, Sergiu M. Dascalu, and Frederick C. Harris, Jr. {\it Towards a Unified Approach for Cross-Platform Software Development}. In {\it Proceedings of the 14th International Conference on Intelligent and Adaptive Systems \& Software Engineering (IASSE-2005)}, Toronto, Canada, July 20--22, 2005,  pp. 235--242.

Deanna M. Needell, Jeff A. Stuart, Tamara C. Thiel, Sergiu M. Dascalu, and Frederick C. Harris, Jr. {\it Software Requirements Specification for a University Class Scheduler}. In {\it Proceedings of The 2003 International Conference on Software Engineering Research and Practice (SERP ‘03)}, June 23--26, 2003, pp. 490--496.
